Hector Permafrost

### 2019-06-04 analysis/paper/paper.Rmd
Add some methods text to manuscript

Several studies have attempted to evaluate the potential economic impacts of current and future permafrost C emissions.
@lawrence_2012_simulation project declines in near-surface permafrost by 33% and 72% in RCP 2.6 and 8.5, respectively, and permafrost C feedback will stabilize at 2100 in RCP 2.6.
More recently, @hope_2015_economic projected permafrost C emissions using the SiBCASA (TODO: write in full) land surface model and used these projections as inputs to the PAGE09 integrated assessment model (IAM).
They found that XXX.
@chen_2019_economic also used PAGE09.
Similarly, @gonzalez-eguino_2016_significant used the DICE (TODO: write in full) model to XXX.
@kessler_2017_estimating also used DICE.

@hope_2015_economic (and others?) rely on climate damage functions of the general form $\delta GDP = f(\delta T)$.
Such functions are, at best, highly uncertain (TODO REF), and possibly conceptually flawed (TODO REF).
(TODO More on this).
GCAM (TODO full name) is an alternative (TODO REF).
(TODO More on GCAM).

@@

@@

## Modeling permafrost emissions

Default heterotrophic respiration ($R$) scheme for a pool $p$ (detritus or soil) in Hector:

This is case 1.

Case 2 uses the same formulation, but splits permafrost C into its own "biome", with its own photosynthesis ($\beta$) and respiration ($Q_{10}$) parameters.

Case 3 extends Case 2 by calculating CO~2~ and CH~4~ emissions as a fraction of the total respiration, controlled by two new parameters $\alpha$ and $\phi$:

>>>>

@@

(TODO: More details on terrestrial C cycle in Hector).
The default heterotrophic respiration ($R$) scheme for a pool $p$ (detritus or soil) in Hector:

## Modeling workflow

We evaluate the sensitivity and parametric uncertainty of three different versions of Hector.

The simplest is the "global" version, which corresponds to the standard version of Hector described in [@hartin_2015_simple].
The global land carbon sink is modeled as a single entity, with parameterizations corresponding to global averages (originally tuned to match global outputs from CMIP5; TODO REF?).
In this configuration, we vary the following parameters:
CO~2~ fertilization effect ($\beta$);
temperature sensitivity of heterotrophic respiration, ($Q^{10}_{RH}$);
fraction of net primary production C that goes to vegetation (`f_nppv`), detritus (`f_nppd`), and soil (`1 - f_nppv - f_nppd`);
and
fraction of vegetation litter C that goes to detritus (`f_litterd`).

The second is the "biome" version, which is the same as the "global" version except that the land carbon sink is divided into two "biomes": "non-permafrost" and "permafrost".
Each of these biomes has its own C pools, fluxes, and parameters.
For this configuration, we varied all of the "global" parameters (previous paragraph) for _both_ biomes ($\beta_{permafrost}$, $\beta_{non-permafrost}$, $Q^10_{RH,permafrost}$, $Q^10_{RH,non-permafrost}$, etc.), as well as the distribution of global pools (vegetation, detritus, soil) and initial primary productivity (`npp_flux0`) aross these two biomes.

The third is the "biome + methane" version.
This version is the same as the "biome" version, but with an additional process that partitions total heterotrophic respiration ($R_{p,tot}$) into a CO~2~ flux ($R_{p, CO_2}$) and a CH~4~ flux ($R_p, CH_4$) as follows:

This process is controlled by two new biome-specific parameters:
$\alpha$ can be interpreted as the fraction of heterotrophic respiration C that is given off as CH~4~ assuming a perfect trade-off between CO~2~ and CH~4~ emissions.
$\phi$ defines the plasticity of this relationship;
at $\phi$ = 1, plasticity is perfect, such that $R_{p,tot}$ is evenly split between CO~2~ and CH~4~;
at $\phi$ = 0, CO~2~ emissions are entirely independent of CH~4~ emissions, such that total C emissions increase linearly with $\alpha$;
at $\phi$ > 1, CO~2~ emissions decline faster than CH~4~ emissions increase.
As such, the total C emissions attributable to heterotrophic respiration are expected to decrease as $\phi$ increases.
In this version of Hector, we varied all of the parameters in the "biome" verson, as well as $\alpha$ and $\phi$ for each biome.

@@
